Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

% We may now prove the undecidability of the three state-resilience problems.
Since the zero-reachability problem for reset-VASS is undecidable \cite{dufourd1998reset}, the reduction implies 
{\sc $t$-liveness} is undecidable.
By reduction to {\sc State-resilience}, and straightforward reduction to the other two state resilience problems, we 
deduce the following.

@@

\mathieu{mettre ici le détail de la  prop5}

@@

\mathieu{mettre ici le détail du Theo 13}

>>>>

% We may now prove the undecidability of the three state-resilience problems.
Since the zero-reachability problem for reset-VASS is undecidable \cite{dufourd1998reset}, the reduction implies 
{\sc $t$-liveness} is undecidable.
We deduce undecidability by reduction to {\sc State-resilience}, and straightforward reductions to the other two state resilience problems, as detailed in Appendix~\ref{appendix}.

@@

Since the zero-reachability problem for reset-VASS is undecidable, the reduction implies {\sc $t$-liveness} is undecidable as well. This leads to the undecidability of {\sc State resilience}, {\sc Bounded-state-resilience} and
{\sc $k$-state-resilience}. 
The first follows straight from Proposition~\ref{reductions},
while the other two
follow from straightforward reductions
we nonetheless
develop in more details here.

@@

% \mathieu{mettre ici le détail du Theo 13}
